---
title: "Publications"
---

<style>
@import url('https://fonts.googleapis.com/css2?family=Latin+Modern+Roman&display=swap');

body {
  font-family: 'Latin Modern Roman', serif;
}

h1, h2, h3, h4, h5, h6 {
  font-family: 'Latin Modern Roman', serif;
}

/* Custom styles for the title */
h1.title {
  font-weight: normal;
  text-align: center;
  margin-bottom: 20px;
}

/* Styles for professional colored boxes with lines under headings/subheadings */
.heading-box {
  padding: 20px;
  margin-bottom: 20px;
  border: 2px solid #333;
  border-radius: 5px;
  background-color: #f5f5f5;
}
.heading-box h2 {
  margin-top: 0;
  margin-bottom: 10px;
  border-bottom: 2px solid #333;
}

.subheading-box {
  padding: 15px;
  margin-bottom: 15px;
  border: 1px solid #555;
  border-radius: 5px;
  background-color: #fafafa;
}
.subheading-box h3 {
  margin-top: 0;
  margin-bottom: 8px;
  border-bottom: 1px solid #555;
}

.subheading-box hr, .heading-box hr {
  border: 0;
  height: 1px;
  background: #ccc;
  margin-bottom: 15px;
}
</style>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(readr)
library(dplyr)
library(purrr)
library(tidyverse)

db <- read.csv("data/pubslist.csv", stringsAsFactors = FALSE)
db$title <- str_to_title(db$title)
```

```{r, results='asis',echo=FALSE, warning=FALSE, message=FALSE}
# Formatting authors
db <- db %>%
  separate(authors, into = c("auth.1", "auth.2", "auth.3", "auth.4"), sep = " and ")
db <- db %>%
  separate(auth.1, into = c("gnam1", "snam1"), sep = " ", extra = "merge")
db <- db %>%
  separate(auth.2, into = c("gnam2", "snam2"), sep = " ", extra = "merge")
db <- db %>%
  separate(auth.3, into = c("gnam3", "snam3"), sep = " ", extra = "merge")
db <- db %>%
  separate(auth.4, into = c("gnam4", "snam4"), sep = " ", extra = "merge")

format_authors <- function(snam1, gnam1, snam2, gnam2, snam3, gnam3, snam4, gnam4) {
  authors <- list()
  if (!is.na(snam1) && !is.na(gnam1)) {
    authors <- c(authors, paste(snam1, gnam1, sep = ", "))
  }
  if (!is.na(gnam2) && !is.na(snam2)) {
    authors <- c(authors, paste(gnam2, snam2, sep = " "))
  }
  if (!is.na(gnam3) && !is.na(snam3)) {
    authors <- c(authors, paste(gnam3, snam3, sep = " "))
  }
  if (!is.na(gnam4) && !is.na(snam4)) {
    authors <- c(authors, paste(gnam4, snam4, sep = " "))
  }
  # Combine authors correctly
  if (length(authors) == 1) {
    return(authors[1])
  } else if (length(authors) > 1) {
    last_author <- authors[length(authors)]
    first_authors <- authors[1:(length(authors) - 1)]
    return(paste(paste(first_authors, collapse = ", "), "and", last_author))
  } else {
    return("")
  }
}

db$authors <- NA

for (i in 1:nrow(db)) {
  db$authors[i] <- format_authors(db$snam1[i], db$gnam1[i], db$snam2[i], db$gnam2[i], db$snam3[i], db$gnam3[i], db$snam4[i], db$gnam4[i])
}
```

```{r, results='asis',echo=FALSE, warning=FALSE, message=FALSE}
# WORKING PAPERS
working.papers <- db %>%
  filter(is.working == 1) %>%
  arrange(desc(year))

# Formatting and outputting the list for working papers
working_papers_formatted <- working.papers %>%
  # Create formatted strings
  mutate(formatted_entry = paste(authors, ". ", year, ". ", '"', title, ".", '" ', "Working Paper.", sep = "")) %>%
  # Extract the formatted_entry column
  pull(formatted_entry)

# Generate HTML for law journals
cat('<div class="heading-box">')
cat('<h2>Academic</h2>')
cat('<div class="subheading-box">')
cat('<h3>Working Papers</h3>')
cat(paste(working_papers_formatted, collapse = "\n\n"))
cat('</div>')
```

```{r, results='asis',echo=FALSE, warning=FALSE, message=FALSE}
# LAW JOURNALS
law.journals <- db %>%
  filter(is.lawj == 1) %>%
  arrange(desc(year))

law.journals.formatted <- law.journals %>%
  mutate(formatted_entry = paste(
    authors, ". ", year, ". ", '"', title, ".", '" ', publication, " ", volume,
    ifelse(!is.na(page.start) & !is.na(page.end), paste0(": ", page.start, "-", page.end), ""),
    ifelse(!is.na(notes), paste0(" (", notes, ")"), ""),
    ".", sep = ""
  )) %>%
  pull(formatted_entry)

cat('<div class="subheading-box">')
cat('<h3>Law Journals</h3>')
cat(paste(law.journals.formatted, collapse = "\n\n"))
cat('</div>')
```

```{r, results='asis',echo=FALSE, warning=FALSE, message=FALSE}
# POLICY JOURNALS
policy.journals <- db %>%
  filter(is.policyj == 1) %>%
  arrange(desc(year))

policy.journals.formatted <- policy.journals %>%
  mutate(formatted_entry = paste(
    authors, ". ", year, ". ", '"', title, ".", '" ', publication, " ", volume,
    ifelse(!is.na(page.start) & !is.na(page.end), paste0(": ", page.start, "-", page.end), ""),
    ifelse(!is.na(notes), paste0(" (", notes, ")"), ""),
    ".", sep = ""
  )) %>%
  pull(formatted_entry)

cat('<div class="subheading-box">')
cat('<h3>Policy Journals</h3>')
cat(paste(policy.journals.formatted, collapse = "\n\n"))
cat('</div></div>')

```

```{r, results='asis',echo=FALSE, warning=FALSE, message=FALSE}
# 50-State Surveys
# Filter and arrange data for 50-State Surveys by year and monthorseason
month_levels <- c("", "January", "February", "March", "April", "May", "June", 
                  "July", "August", "September", "October", "November", "December", 
                  "Spring")

fifty_state_surveys <- db %>%
  filter(is.50statesurvey == 1) %>%
  # Convert monthorseason to factor with custom order
  mutate(monthorseason = factor(monthorseason, levels = month_levels, ordered = TRUE)) %>%
  arrange(desc(year), desc(monthorseason))

# Function to format a single entry for 50-State Surveys
format_entry_fifty_state_survey <- function(authors, monthorseason, year, title, publication) {
  # Author
  author_formatted <- authors
  
  # Month or season
  monthorseason_formatted <- if (!is.na(monthorseason) && monthorseason != "") paste0(monthorseason, " ") else ""
  
  # Year
  year_formatted <- if (!is.na(year) && year != "") paste0(year, ". ") else ""
  
  # Title
  title_formatted <- if (!is.na(title) && title != "") paste0('"', title, '." ') else ""
  
  # Publication
  publication_formatted <- if (!is.na(publication) && publication != "") publication else ""
  
  # Combine into formatted string for the entry
  entry <- paste0(author_formatted, ". ", monthorseason_formatted, year_formatted, title_formatted, publication_formatted, ".")

  return(entry)
}

# Apply formatting to each 50-State Survey entry
fifty_state_survey_entries <- fifty_state_surveys %>%
  mutate(formatted_entry = pmap_chr(list(authors, monthorseason, year, title, publication), format_entry_fifty_state_survey))

# Generate HTML for 50-State Surveys
cat('<div class="heading-box">')
cat('<h2>Grey Literature</h2>')
cat('<div class="subheading-box">')
cat('<h3>50-State Surveys</h3>')
cat(paste(fifty_state_survey_entries$formatted_entry, collapse = "\n\n"))
cat('</div>')
```

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Magazine articles
magazine_articles <- db %>%
  filter(is.mag == 1) %>%
  mutate(monthorseason = factor(monthorseason, levels = month_levels, ordered = TRUE)) %>%
  arrange(desc(year), desc(monthorseason))

# Function to format a single entry for Magazine Articles
format_entry_magazine_article <- function(authors, monthorseason, year, title, publication) {
  # Author
  author_formatted <- authors
  
  # Month or season
  monthorseason_formatted <- if (!is.na(monthorseason) && monthorseason != "") paste0(monthorseason, " ") else ""
  
  # Year
  year_formatted <- if (!is.na(year) && year != "") paste0(year, ". ") else ""
  
  # Title
  title_formatted <- if (!is.na(title) && title != "") paste0('"', title, '" ') else ""
  # Publication
  publication_formatted <- if (!is.na(publication) && publication != "") publication else ""
  # Combine into formatted string for the entry
  entry <- paste0(author_formatted, ". ", monthorseason_formatted, year_formatted, title_formatted, publication_formatted, ".")

  return(entry)
}

# Apply formatting to each Magazine Article entry
magazine_article_entries <- magazine_articles %>%
  mutate(formatted_entry = pmap_chr(list(authors, monthorseason, year, title, publication), format_entry_magazine_article))

# Generate HTML for Magazine Articles
cat('<div class="subheading-box">')
cat('<h3>Magazine Articles</h3>')
cat(paste(magazine_article_entries$formatted_entry, collapse = "\n\n"))
cat('</div>')
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Two-Page Issue Briefs
issue_briefs <- db %>%
  filter(is.legisbrief == 1) %>%
  mutate(monthorseason = factor(monthorseason, levels = month_levels, ordered = TRUE)) %>%
  arrange(desc(year), desc(monthorseason))

# Function to format a single entry for Two-Page Issue Briefs
format_entry_issue_brief <- function(authors, monthorseason, year, title, publication) {
  # Author
  author_formatted <- authors
  # Month or season
  monthorseason_formatted <- if (!is.na(monthorseason) && monthorseason != "") paste0(monthorseason, " ") else ""
  # Year
  year_formatted <- if (!is.na(year) && year != "") paste0(year, ". ") else ""
  
  # Title
  title_formatted <- if (!is.na(title) && title != "") paste0('"', title, '." ') else ""

  # Publication
  publication_formatted <- if (!is.na(publication) && publication != "") publication else ""
  
  # Combine into formatted string for the entry
  entry <- paste0(author_formatted, ". ", monthorseason_formatted, year_formatted, title_formatted, publication_formatted, ".")

  return(entry)
}

# Apply formatting to each Two-Page Issue Brief entry
issue_brief_entries <- issue_briefs %>%
  mutate(formatted_entry = pmap_chr(list(authors, monthorseason, year, title, publication), format_entry_issue_brief))

# Generate HTML for Two-Page Issue Briefs
cat('<div class="subheading-box">')
cat('<h3>Two-Page Issue Briefs</h3>')
cat(paste(issue_brief_entries$formatted_entry, collapse = "\n\n"))
cat('</div>')
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Filter for podcasts
podcasts <- db %>%
  filter(is.pod == 1) %>%
  mutate(monthorseason = factor(monthorseason, levels = month_levels, ordered = TRUE)) %>%
  arrange(desc(year), desc(monthorseason))

# Function to format a single entry for Podcasts
format_entry_podcast <- function(authors, monthorseason, year, title, publication) {
  # Author
  author_formatted <- authors
  
  # Month or season
  monthorseason_formatted <- if (!is.na(monthorseason) && monthorseason != "") paste0(monthorseason, " ") else ""
  
  # Year
  year_formatted <- if (!is.na(year) && year != "") paste0(year, ". ") else ""
  
  # Title in title case
  title_formatted <- if (!is.na(title) && title != "") paste0('"', tools::toTitleCase(title), '." ') else ""

  # Publication
  publication_formatted <- if (!is.na(publication) && publication != "") publication else ""
  
  # Combine into formatted string for the entry
  entry <- paste0(author_formatted, ". ", monthorseason_formatted, year_formatted, title_formatted, publication_formatted, ".")

  return(entry)
}

# Apply formatting to each Podcast entry
podcast_entries <- podcasts %>%
  mutate(formatted_entry = pmap_chr(list(authors, monthorseason, year, title, publication), format_entry_podcast))

# Generate HTML for Podcasts
cat('<div class="subheading-box">')
cat('<h3>Podcasts</h3>')
cat(paste(podcast_entries$formatted_entry, collapse = "\n\n"))
cat('</div>')
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Load tools package for toTitleCase function
library(tools)

# Blog Posts
blog_posts <- db %>%
  filter(is.blog == 1) %>%
  mutate(monthorseason = factor(monthorseason, levels = month_levels, ordered = TRUE)) %>%
  arrange(desc(year), desc(monthorseason))

# Function to format a single entry for Blog Posts
format_entry_blog_post <- function(authors, monthorseason, year, title, publication) {
  # Author
  author_formatted <- authors
  
  # Month or season
  monthorseason_formatted <- if (!is.na(monthorseason) && monthorseason != "") paste0(monthorseason, " ") else ""
  
  # Year
  year_formatted <- if (!is.na(year) && year != "") paste0(year, ". ") else ""
  
  # Title in title case
  title_formatted <- if (!is.na(title) && title != "") paste0('"', tools::toTitleCase(title), '." ') else ""

  # Publication
  publication_formatted <- if (!is.na(publication) && publication != "") publication else ""
  
  # Combine into formatted string for the entry
  entry <- paste0(author_formatted, ". ", monthorseason_formatted, year_formatted, title_formatted, publication_formatted, ".")

  return(entry)
}

# Apply formatting to each Blog Post entry
blog_post_entries <- blog_posts %>%
  mutate(formatted_entry = pmap_chr(list(authors, monthorseason, year, title, publication), format_entry_blog_post))

# Generate HTML for Blog Posts
cat('<div class="subheading-box">')
cat('<h3>Blog Posts</h3>')
cat(paste(blog_post_entries$formatted_entry, collapse = "\n\n"))
cat('</div>')
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Load tools package for toTitleCase function
library(tools)

# Think Tank Papers
think_tank_papers <- db %>%
  filter(is.thinktank == 1) %>%
  mutate(monthorseason = factor(monthorseason, levels = month_levels, ordered = TRUE)) %>%
  arrange(desc(year), desc(monthorseason))

# Function to format a single entry for Think Tank Papers
format_entry_think_tank_paper <- function(authors, monthorseason, year, title, publication, notes) {
  # Author
  author_formatted <- authors
  
  # Month or season
  monthorseason_formatted <- if (!is.na(monthorseason) && monthorseason != "") paste0(monthorseason, " ") else ""
  
  # Year
  year_formatted <- if (!is.na(year) && year != "") paste0(year, ". ") else ""
  
  # Title in title case
  title_formatted <- if (!is.na(title) && title != "") paste0('"', tools::toTitleCase(title), '." ') else ""

  # Publication
  publication_formatted <- if (!is.na(publication) && publication != "") publication else ""
  
  # Notes
  notes_formatted <- if (!is.na(notes) && notes != "") paste0(" (", notes, ")") else ""
  
  # Combine into formatted string for the entry
  entry <- paste0(author_formatted, ". ", monthorseason_formatted, year_formatted, title_formatted, publication_formatted, notes_formatted, ".")

  return(entry)
}

# Apply formatting to each Think Tank Paper entry
think_tank_paper_entries <- think_tank_papers %>%
  mutate(formatted_entry = pmap_chr(list(authors, monthorseason, year, title, publication, notes), format_entry_think_tank_paper))

# Generate HTML for Think Tank Papers
cat('<div class="subheading-box">')
cat('<h3>Papers</h3>')
cat(paste(think_tank_paper_entries$formatted_entry, collapse = "\n\n"))
cat('</div>')
```

